Survivable Set Connectivity

### 2015-05-13 draft.tex
not sure what changes i made
minor changes to intro

Note that a ``path between $S_i$ and $T_i$" refers to any path that connects a vertex in $S_i$ to a vertex in $T_i$.

@@

The paper is organized as follows. Sections 2, 3, and 4 provide the background necessary to understand the algorithm by Chalermsook et al. In Section 2, we present a natural integer linear programming formulation of the problem. Then, in Section 3, we introduce the idea of a \emph{tree embedding}, which allows us to transform arbitrary graphs $G$ into trees that can be more easily handled by the algorithm. In Section 4, we give a rounding scheme by Garg et al. known as RoundGKR, which the algorithm uses as a black box \cite{GKR}. We then pull together these concepts in Section 5 to present and analyze the approximation algorithm for SSC by Chalermsook et al. Finally, in Section 6, we present a slight modification to the algorithm which improves the approximation ratio under special circumstances. We also conclude with ideas for further improvements.

@@

The objective function $\sum c(x) x_e$ simply minimizes the cost of all edges included in $H$. The constraint ensures that for all pairs $(S_i,T_i)$, any cut where $S_i$ is on one side of the cut and $T_i$ is on the other side has at least $k$ edges crossing the cut. This property holds if and only if there are $k$ edge disjoint paths from $S_i$ to $T_i$. 
%
%
% 
%This cut-based integer linear program finds exactly $H$. To see why the constraints ensure that each $(S_i, T_i)$ pair has at least $k$ edge disjoint paths, we can look at the cuts corresponding to $S_i$ and $T_i$. First, we let $S = S_i$, then there are $k$ outgoing edges. We can choose to include one more node to $S$, following a particular outgoing edge of the cut in $H$. We can continue doing this until we reach $T_i$. This will trace out a path between $S_i$ and $T_i$. If we do this for each edge, and then we do this for each $(S_i, T_i)$ pair, we can confirm that there are in fact $k$ edge-disjoint paths between each $(S_i, T_i)$ pair.

>>>>

Note that a ``path between $S_i$ and $T_i$" refers to any path that connects a vertex in $S_i$ to a vertex in $T_i$. The cost of a subgraph is simply the sum of the cost of the subgraph edges.

@@

The paper is organized as follows. Sections 2, 3, and 4 provide the background necessary to understand the algorithm by Chalermsook et al. In Section 2, we present a natural integer linear programming formulation of the problem. Then, in Section 3, we introduce the idea of a \emph{tree embedding}, which allows us to transform arbitrary graphs $G$ into trees that can be more easily handled by the algorithm. In Section 4, we give a rounding scheme by Garg et al. known as RoundGKR, which the algorithm uses as a black box \cite{GKR}. We then pull together these concepts in Section 5 to present and analyze the approximation algorithm for SSC by Chalermsook et al. Finally, in Section 6, we present our own modification to the algorithm which improves the approximation ratio under special circumstances. We also conclude with ideas for potential further improvements.

@@

The objective function $\sum c(x) x_e$ simply minimizes the cost of all edges included in $H$. The constraint ensures that for all pairs $(S_i,T_i)$, any cut where $S_i$ is on one side of the cut and $T_i$ is on the other side has at least $k$ edges crossing the cut. We claim (but do not prove) that this property holds if and only if there are $k$ edge disjoint paths from $S_i$ to $T_i$. 
%
%
% 
%This cut-based integer linear program finds exactly $H$. To see why the constraints ensure that each $(S_i, T_i)$ pair has at least $k$ edge disjoint paths, we can look at the cuts corresponding to $S_i$ and $T_i$. First, we let $S = S_i$, then there are $k$ outgoing edges. We can choose to include one more node to $S$, following a particular outgoing edge of the cut in $H$. We can continue doing this until we reach $T_i$. This will trace out a path between $S_i$ and $T_i$. If we do this for each edge, and then we do this for each $(S_i, T_i)$ pair, we can confirm that there are in fact $k$ edge-disjoint paths between each $(S_i, T_i)$ pair.
